Hypertension and microbiome

### 2019-08-28 articletwo-sensitivityanalysis.Rmd
99 permutaions on sensitivity

```{r my variables}
var.BP <- c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")
var.CL.min <- c("BL_AGE", "SEX")
var.CL <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB",
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
var.CL.opt <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB", "BP_TREAT")
permutations <- 3
```

>>>>

```{r my variables}
var.BP <- c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")
var.CL.min <- c("BL_AGE", "SEX")
var.CL <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB",
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
var.CL.opt <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB", "BP_TREAT")
permutations <- 99
```
